---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

# unirankings: Comparing University Rankings of Different Countries

<!-- badges: start -->
<!-- badges: end -->

Comparing the cumulative distribution functions of university rankings among 4 countries: Switzerland, Germany, France, and the US.

## Introduction

## Data

* [qsrankings14.csv](https://github.com/zambujo/unirankings/blob/master/qsrankings14.csv)  
  Source: [QS World University Rankings  2014/15](http://www.topuniversities.com/university-rankings/world-university-rankings/2014)

* [cwur.csv](https://github.com/zambujo/unirankings/blob/master/cwur.csv)  
  Source: [Center for World University Rankings](http://cwur.org/2014/)

* [cwts.csv](https://github.com/zambujo/unirankings/blob/master/cwts.csv)  
  Source: [CWTS Leiden rankings](http://www.leidenranking.com/ranking/2014)

## Usage

To run the R scripts in the R folder, you need the following libraries:

```{r}
shhh <- suppressPackageStartupMessages
shhh(library(tidyverse))
shhh(library(here))
```


## Result

[QS rankings QQ plot](qs-qqplot.svg)

## License

`unirankings` is released under the [MIT License](./LICENCE.md).
