---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# unirankings: Comparing University Rankings of Different Countries

<!-- badges: start -->
<!-- badges: end -->

Quick comparison of the distributions of QS university rankings among a number of countries.

## Introduction

## Data

* [QS rankings](https://github.com/zambujo/unirankings/blob/master/data/qs.csv) from [QS World University Rankings  2020/21](http://www.topuniversities.com/university-rankings/world-university-rankings)

## Usage

* Make sure you have the following libraries:  

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(jsonlite)
library(janitor)
library(countrycode)
library(here)
library(conflicted)
```

> Optionally, sort out the most likely conflicts: 

```{r, message=FALSE}
conflict_prefer('flatten', 'purrr')
conflict_prefer('filter', 'dplyr')
conflict_prefer('lag', 'dplyr')
```

* To update the data, run:

```{r, eval=FALSE}
source(here("R", "read.R"))
```

* To summarize the data by country, run:

```{r, eval=FALSE}
source(here("R", "logic.R"))
```

## Result

```{r, message=FALSE, warning=FALSE}
df <- read_csv(here("data", "qs.csv"))
country_summary <- read_csv(here("data", "country_summary.csv"))
```


```{r, message=FALSE, warning=FALSE}
country_summary %>% 
  filter(count_score >= 5) %>% 
  arrange(desc(median_score)) %>%
  select(country, `n(scores)` = count_score, `med(score)` = median_score) %>%
  head(10) %>%
  knitr::kable()
```


```{r boxplots, message=FALSE, warning=FALSE, fig.asp=0.618, fig.align='center'}
df %>% 
  filter(country %in% c("CH", "FR", "NL", "US", "GB", "DE")) %>%
  ggplot(aes(score, country)) +
  labs(
    title = "QS University Score Distribution Per Country",
    subtitle = "For CH, DE, FR, GB, NL, and the US") +
  geom_boxplot(varwidth = TRUE)
```

## License

`unirankings` is released under the [MIT License](./LICENCE.md).
